### 2020-02-10 README.Rmd
Partial version of summarize_oolong

>>>>

## Suggested workflow

The test makes more sense if more than one coder is involved. A suggested workflow is to create the test, then clone the oolong object. Ask multiple coders to do the test(s) and then summarize the results.

Create a new oolong object.

```{r step1}
oolong_test_rater1 <- create_oolong(newsgroup_stm)
```

Clone the oolong object to be used by other raters.

```{r step2}
oolong_test_rater2 <- clone_oolong(oolong_test_rater1)
```

Ask different coders to code each object and then lock the object.

```{r, eval = FALSE}
## Let rater 1 do the test.
oolong_test_rater1$do_word_intrusion_test()
oolong_test_rater1$lock()

## Let rater 2 do the test.
oolong_test_rater2$do_word_intrusion_test()
oolong_test_rater2$lock()
```

```{r, include = FALSE}
### Mock this process
oolong_test_rater1$.__enclos_env__$private$test_content$word$answer <- oolong_test_rater1$.__enclos_env__$private$test_content$word$intruder
oolong_test_rater1$lock()
oolong_test_rater2$.__enclos_env__$private$test_content$word$answer <- oolong_test_rater2$.__enclos_env__$private$test_content$word$intruder
oolong_test_rater2$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
oolong_test_rater2$lock()
```

Get a summary of the two objects.

```{r, step3}
summarize_oolong(oolong_test_rater1, oolong_test_rater2)
```
